The Shades of Racism in the Beauty Industry

### 2023-04-19 outputs/paper/paper.qmd
final edits
final adjustments to the intro and references

The makeup industry specifically has seen a lot of growth with the arrival of Sephora and Ulta, large retailers who host the products of a variety of brands both low and high end. This has popularized the notion of "indie brands", who have gained popularity by prioritizing high quality ingredients and affordability, allowing more people access to better products. However, all aspects of the beauty space still remain hesitant to uplift and empower people of all walks of life, especially people of color. 
The purpose of this paper is to explore the impact of the beauty industry's historically racist standards, and to explore whether they are still in place today. It is the fashion and makeup industry that will be the primary focus of this analysis. To explore racism in the fashion industry, the heart of the fashion culture, the covers of high fashion magazine Vogue, will be studied. The complexions of the models on the Vogue covers from 2000 to 2018 will be analyzed in order to extrapolate the inclusivity of the future of fashion. To analyze the makeup industry, the most popular foundation lines of the top beauty brands in the United States will be studied to explore the distribution of shades across the various complexions to see how many people of color are supported and provided for.

@@

There are a few weaknesses and limitations in this paper. Firstly, our analysis only covers representation in fashion culture and the range of products available in the makeup industry. Analysis can and should be done in other areas of the beauty industry, on both the product and service side. Secondly, there are limitations in the calculation of the lightness value. It does not include the various undertones in skin, and difference in makeup products and ingredients needed for people with deeper complexions. It is often the case that while some brands may offer foundation shades that are darker, but that does not mean that those shades are usable. Lack of research on the needs of people of color that often results in foundation shades that are the wrong undertone, too grey, orange, or red. The same goes for the lightness value calculation off of the Vogue covers. Vogue covers are heavily edited, with a team behind them for camera work, lighting, and editing. This could have skewed the depth of the complexion of the deeper skinned models, since according to @fig-all_white, there is a great deal of fluctuation in the skin tone to get an accurate understanding. Next steps would include using the hex code of the models foundation shade to get a more accurate representation of skin tone.

>>>>

The makeup industry specifically has seen a lot of growth with the arrival of Sephora and Ulta, large retailers who host the products of a variety of brands both low and high end. This has popularized the notion of "indie brands", who have gained popularity by prioritizing high quality ingredients and affordability, allowing more people access to better products. However, all aspects of the beauty space still remain hesitant to uplift and empower people of all walks of life, especially people of color. 
The purpose of this paper is to explore the impact of the beauty industry's historically racist standards, and to explore whether they are still in place today. It is the fashion and makeup industry that will be the primary focus of this analysis. To explore racism in the fashion industry, the heart of the fashion culture, the covers of high fashion magazine Vogue, will be studied. The complexions of the models on the Vogue covers from 2000 to 2018 will be analyzed in order to extrapolate the inclusivity of the future of fashion. To analyze the makeup industry, the most popular foundation lines of the top beauty brands in the United States will be studied to explore the distribution of shades across the various complexions to see how many people of color are supported and provided for.This paper explores the estimand how does the lightness value of an individuals complexion impact your representation and the products made available for you in the fashion and makeup industry.

@@

There are a few weaknesses and limitations in this paper. Firstly, the analysis only covers representation in fashion culture and the range of products available in the makeup industry. Analysis can and should be done in other areas of the beauty industry, on both the product and service side. Secondly, there are limitations in the calculation of the lightness value. It does not include the various undertones in skin, and difference in makeup products and ingredients needed for people with deeper complexions. It is often the case that while some brands may offer foundation shades that are darker, but that does not mean that those shades are usable. Lack of research on the needs of people of color that often results in foundation shades that are the wrong undertone, too grey, orange, or red. The same goes for the lightness value calculation off of the Vogue covers. Vogue covers are heavily edited, with a team behind them for camera work, lighting, and editing. This could have skewed the depth of the complexion of the deeper skinned models, since according to @fig-all_white, there is a great deal of fluctuation in the skin tone to get an accurate understanding. Next steps would include using the hex code of the models foundation shade to get a more accurate representation of skin tone.
